---
title: "The Impact of Coffee Features on Quality Classification"
author: "Group_15"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval=TRUE, include=FALSE}
library(tidyverse)
library(readxl)
library(gridExtra)
library(ggplot2)
library(skimr)
library(kableExtra)
library(car)
library(ROCR)
library(GGally)
```

# Data Introduction

This data come from the Coffee Quality Database (CQD). The database contains information from the CoffeevQuality Institute which is a non-profit organisation working internationally to improve the quality of coffee and thelives of the people who produce it. Each of the 5 datasets contain information on features of coffee and its production includinan overall score of quality. 
• *country_of_origin* -- Country where the coffee bean originates from. 
• *aroma* -- Aroma grade (ranging from 0-10) 
• *flavor* -- Flavour grade (ranging from 0-10) 
• *acidity* -- Acidity grade (ranging from 0-10) 
• *category_two_defects* -- Count of category 2 type defects in the batch of coffee beans tested. 
• *altitiude_mean_meters* -- Mean altitude of the growers farm (in metres)
• *harvested* -- Year the batch was harvested 
• *Qualityclass* -- Quality score for the batch (Good - ≥ 82.5, Poor - \<82.5).

# Data Cleaning

First clear the null lines in the data, and then delete all lines with the line name *Taiwan* since *Taiwan* is not a country.

```{r echo = TRUE, results='hide'}
#coffee.data <- read.csv("dataset15.csv")
coffee.data <- read.csv("dataset15.csv")
coffee <- na.omit(coffee.data)
coffee<- subset(coffee, country_of_origin != 'Taiwan')
coffee
```

Using Qualityclass as a classification variable, assign Qualityclass 0 and 1 in terms of it's original value poor and good.

```{r pressure, echo=TRUE, results='hide'}
coffee$Qualityclass <- as.integer(coffee$Qualityclass == "Good")
coffee

```

A subset with reasonable data distribution is selected from *coffee.data's* data set and stored in a new data set, *coffee*.

```{r echo = TRUE, results='hide'}
quantiles_aroma <- quantile(coffee.data$aroma,probs=c(0.25,0.75),na.rm=FALSE)
```

## Correlation Test
Correlation test for eight variables:
```{r echo=TRUE, results='hide'}
coffee_nocountry <- coffee[,-which(names(coffee) == "country_of_origin")]
ggpairs(coffee_nocountry) +
  theme(plot.background = element_rect(
    fill = "transparent",
    colour = NA,
    size = 1))
```

## Cleaning outliers
The IQR method is used to identify outliers in coffee. 
The IQR (interquartile range) is a measure of the spread of the middle 50% of the numeric variables in coffee, calculated as the difference between the third quartile (Q3) and the first quartile (Q1) of the dataset.
According to the results of the correlation test, we decided to clean up the outliers only for the three variables aroma, flavor, and acidity.

```{r echo=TRUE, results='hide'}
quantiles_aroma <- quantile(coffee$aroma,probs=c(0.25,0.75),na.rm=FALSE)
IQR_aroma <- IQR(coffee$aroma)
Lower_aroma <- quantiles_aroma[1]-1.5*IQR_aroma
Upper_aroma <- quantiles_aroma[2]+1.5*IQR_aroma
coffee<- subset(coffee,coffee$aroma>Lower_aroma & coffee$aroma< Upper_aroma)

quantiles_flavor <- quantile(coffee$flavor,probs=c(0.25,0.75),na.rm=FALSE)
IQR_flavor <- IQR(coffee$flavor)
Lower_flavor <- quantiles_flavor[1]-1.5*IQR_flavor
Upper_flavor <- quantiles_flavor[2]+1.5*IQR_flavor
coffee<- subset(coffee,coffee$flavor>Lower_flavor & coffee$flavor< Upper_flavor)

quantiles_acidity <- quantile(coffee$acidity,probs=c(0.25,0.75),na.rm=FALSE)
IQR_acidity <- IQR(coffee$acidity)
Lower_acidity <- quantiles_acidity[1]-1.5*IQR_acidity
Upper_acidity <- quantiles_acidity[2]+1.5*IQR_acidity
coffee<- subset(coffee,coffee$acidity>Lower_acidity & coffee$acidity< Upper_acidity)
coffee

```

## Store the cleared data

```{r}
write.csv(coffee,file="coffee_clean.csv",row.names=FALSE)
```

# Correlation test between variables

```{r echo = FALSE}
coffee.clean <- read.csv("coffee_clean.csv")
cor(coffee[,2:7])
```


# Data visualization


```{r echo = FALSE}
library(gridExtra)
coffee$Qualityclass <- factor(coffee$Qualityclass)
plot1 <- ggplot(data = coffee,aes(x = Qualityclass, y = aroma, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Aroma") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot2 <- ggplot(data = coffee,aes(x = Qualityclass, y = flavor, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Flavor") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot3 <- ggplot(data = coffee,aes(x = Qualityclass, y = acidity, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Acidity") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot4 <- ggplot(data = coffee,aes(x = Qualityclass, y = category_two_defects, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Category_two_defects") + 
  ylim(-1,10) + 
  theme(legend.position = "none")

plot5 <- ggplot(data = coffee,aes(x = Qualityclass, y = altitude_mean_meters, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Altitude_mean_meters") + 
  ylim(0,2000)
  theme(legend.position = "none")


## The number of different quality inspection results in each year
plot6 <- ggplot(coffee, aes(x=harvested, fill=as.factor(Qualityclass))) +
  geom_bar(position="dodge", alpha=0.8, stat="count") +
  scale_fill_manual(values=c("Orange", "Blue")) +
  labs(x="Harvested", y="Count", fill="Qualityclass") +
  ggtitle("Qualityclass count by Harvest")

## Merge six charts
## Arrange plot1 to plot6 in a grid of 2 rows and 3 columns
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, nrow=3, ncol=2)
```

# Standardized data

```{r echo = TRUE, results='hide'}
## Creates a logical vector that determines which columns in the data box coffee contain numeric data. It uses the function sapply to determine whether the data type of each column is numeric.
numeric_cols <- sapply(coffee,is.numeric)
## The columns containing only numerical data in data box coffee are extracted and assigned to new data box numeric_coffee
numeric_coffee <- coffee[,numeric_cols]
## A new data box scaled_coffee is obtained by standardizing numerical data in numeric_coffee. The standardization process is to transform the data range of different variables into the same scale for easy comparison.
scaled_coffee <- as.data.frame(scale(numeric_coffee))
## Add the category_two_defects column from the original data box coffee to scaled_coffee.
scaled_coffee$category_two_defects <- coffee$category_two_defects
## Assign the numerical data in the standardized data frame scaled_coffee back to the corresponding column in the original data frame coffee, and overwrite the original data.
coffee[,numeric_cols] <- scaled_coffee
coffee
```

# Modeling

```{r echo=TRUE, include=FALSE}
model1 <- glm(Qualityclass~aroma+flavor+acidity,family=binomial(link="logit"), data=coffee)
model2 <- glm(Qualityclass~aroma,family=binomial(link="logit"),
              data=coffee)
model3 <- glm(Qualityclass~flavor,family=binomial(link="logit"),
              data=coffee)
model4 <- glm(Qualityclass~acidity,family=binomial(link="logit"),
              data=coffee)
model5 <- glm(Qualityclass~aroma+flavor,family=binomial(link="logit"),
              data=coffee)
model6 <- glm(Qualityclass~flavor+acidity,family=binomial(link="logit"),
              data=coffee)
model7 <- glm(Qualityclass~aroma+acidity,family=binomial(link="logit"),
              data=coffee)
model8 <- glm(Qualityclass~aroma*flavor+acidity,family=binomial(link="logit"),
              data=coffee)
model9 <- glm(Qualityclass~aroma+flavor*acidity,family=binomial(link="logit"),
              data=coffee)
model10 <- glm(Qualityclass~aroma*acidity+flavor,family=binomial(link="logit"),
              data=coffee)
model11 <- glm(Qualityclass~aroma*flavor+aroma*acidity,family=binomial(link="logit"),
              data=coffee)
model12 <- glm(Qualityclass~aroma*flavor+acidity*flavor,family=binomial(link="logit"),
              data=coffee)
model13 <- glm(Qualityclass~aroma*acidity+flavor*acidity,family=binomial(link="logit"),
              data=coffee)
model14 <- glm(Qualityclass~aroma*flavor+acidity*flavor+acidity*aroma,family=binomial(link="logit")
               ,data=coffee)
model15 <- glm(Qualityclass~aroma*flavor*acidity,family=binomial(link="logit"),
              data=coffee)
anova(model1,model2,model3,model4,model5,
      model6,model7,model8,model9,model10,
      model11,model12,model13,model14,model15)
summary(model9)
AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)
AIC(model5)
AIC(model6)
AIC(model7)
AIC(model8)
AIC(model9)
AIC(model10)
AIC(model11)
AIC(model12)
AIC(model13)
AIC(model14)
AIC(model15)


```


```{r echo=TRUE}
Modelname <- c("model1","model2","model3","model4",
                         "model5","model6","model7","model8",
                         "model9","model10","model11","model12",
                         "model13","model14","model15")
AIC <- c(model1$aic,model2$aic,model3$aic,model4$aic,
         model5$aic,model6$aic,model7$aic,model8$aic,
         model9$aic,model10$aic,model11$aic,model12$aic,
         model13$aic,model14$aic,model15$aic)
Deviance <- c(model1$deviance,model2$deviance,model3$deviance,
              model4$deviance,model5$deviance,model6$deviance,
              model7$deviance,model8$deviance,model9$deviance,
              model10$deviance,model11$deviance,model12$deviance,
              model13$deviance,model14$deviance,model15$deviance)
table_values <- data.frame(Modelname, Deviance, AIC)
table_values <- as.data.frame(table_values)
table_values %>%
  transmute(Modelname=Modelname, Deviance=Deviance, AIC=AIC) %>%
  kable(caption = '\\label{tab:summary} AIC of each model',
booktabs = TRUE, linesep = "", digits = 2) %>%
  kable_styling(font_size = 16, latex_options = "hold_position")

```

# Multicollinearity test of model

```{r echo=TRUE}
vif(model1)
vif(model5)
vif(model6)
vif(model7)
vif(model8)
vif(model9)
vif(model10)
vif(model11)
vif(model12)
vif(model13)
vif(model14)
vif(model15)
```
Receiver Operating Characteristic (ROC) curve shows the performance of a model1. 
The area under the ROC curve (AUC) is 0.94, which indicates a good classification performance.

```{r echo=TRUE}
coffee.pr <- predict(model1, type="response")
score <- prediction(coffee.pr,coffee$Qualityclass)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
p1 <- ggplot(perfd, aes(x= x, y=y)) + geom_line() +
  xlab("False positive rate") + ylab("True positive rate") +
  ggtitle(paste("Area under the curve:", round(auc@y.values[[1]], 3)))
p1
```




