---
title: "The Impact of Coffee Features on Quality Classification"
author: "Group_15"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
  html_document:
    df_print: paged
  md_document:
    variant: markdown_github
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval=TRUE, warning=FALSE, message=FALSE,include=FALSE}
library(tidyverse)
library(readxl)
library(gridExtra)
library(ggplot2)
library(skimr)
library(kableExtra)
library(car)
library(ROCR)
library(GGally)
```

# Data Introduction

This data come from the Coffee Quality Database (CQD). The database contains information from the CoffeevQuality Institute which is a non-profit organisation working internationally to improve the quality of coffee and the lives of the people who produce it. Each of the 5 datasets contain information on features of coffee and its production including an overall score of quality.



Variable                  | Explanation    
:------------------------:|:------------------------------
  country_of_origin       |Country where the coffee bean originates from. 
  aroma                   |Aroma grade (ranging from 0-10) 
  flavor                  |Flavour grade (ranging from 0-10) 
  acidity                 |Acidity grade (ranging from 0-10) 
  category_two_defects    |Count of category 2 type defects in the batch of coffee beans tested. 
  altitude_mean_meters    |Mean altitude of the growers farm (in metres)
  harvested               |Year the batch was harvested 
  Qualityclass            |Quality score for the batch (Good - >= 82.5, Poor - \<82.5).
Table: \label{tab:BEofD}Brief Explanation of the Data.

# Data Cleaning

First clear the null lines in the data, and then delete all lines with the line name *Taiwan* since *Taiwan* is not a country.

```{r echo = TRUE, warning=FALSE, message=FALSE, results='hide'}
#coffee.data <- read.csv("dataset15.csv")
coffee.data <- read.csv("C:/Users/hello/Downloads/dataset15.csv")
coffee <- na.omit(coffee.data)
coffee<- subset(coffee, country_of_origin != 'Taiwan')
```

Using Qualityclass as a classification variable, assign Qualityclass 0 and 1 in terms of it's original value poor and good.

```{r pressure, echo=TRUE, warning=FALSE, message=FALSE,results='hide'}
coffee$Qualityclass <- as.integer(coffee$Qualityclass == "Good")
```

A subset with reasonable data distribution is selected from *coffee.data's* data set and stored in a new data set, *coffee*.

```{r echo = TRUE, warning=FALSE, message=FALSE,results='hide'}
quantiles_aroma <- quantile(coffee.data$aroma,probs=c(0.25,0.75),na.rm=FALSE)
```

## Correlation Test
Correlation test for eight variables:
```{r echo=TRUE, warning=FALSE, message=FALSE,results='hide'}
coffee_nocountry <- coffee[,-which(names(coffee) == "country_of_origin")]
ggpairs(coffee_nocountry) +
  theme(plot.background = element_rect(
    fill = "transparent",
    colour = NA,
    size = 1))
```
From the results of the correlation test, only aroma, flavor, and acidity are highly correlated with Qualityclass, while the correlation between category_two_defects, altitude_mean_meters, harvested, and Qualityclass is very low.

## Cleaning outliers
The IQR method is used to identify outliers in coffee. 
The IQR (interquartile range) is a measure of the spread of the middle 50% of the numeric variables in coffee, calculated as the difference between the third quartile (Q3) and the first quartile (Q1) of the dataset.
According to the results of the correlation test, we decided to clean up the outliers only for the three variables aroma, flavor, and acidity.

```{r echo=TRUE, warning=FALSE, message=FALSE,results='hide'}
quantiles_aroma <- quantile(coffee$aroma,probs=c(0.25,0.75),na.rm=FALSE)
IQR_aroma <- IQR(coffee$aroma)
Lower_aroma <- quantiles_aroma[1]-1.5*IQR_aroma
Upper_aroma <- quantiles_aroma[2]+1.5*IQR_aroma
coffee<- subset(coffee,coffee$aroma>Lower_aroma & coffee$aroma< Upper_aroma)

quantiles_flavor <- quantile(coffee$flavor,probs=c(0.25,0.75),na.rm=FALSE)
IQR_flavor <- IQR(coffee$flavor)
Lower_flavor <- quantiles_flavor[1]-1.5*IQR_flavor
Upper_flavor <- quantiles_flavor[2]+1.5*IQR_flavor
coffee<- subset(coffee,coffee$flavor>Lower_flavor & coffee$flavor< Upper_flavor)

quantiles_acidity <- quantile(coffee$acidity,probs=c(0.25,0.75),na.rm=FALSE)
IQR_acidity <- IQR(coffee$acidity)
Lower_acidity <- quantiles_acidity[1]-1.5*IQR_acidity
Upper_acidity <- quantiles_acidity[2]+1.5*IQR_acidity
coffee<- subset(coffee,coffee$acidity>Lower_acidity & coffee$acidity< Upper_acidity)


# Store the cleared data
write.csv(coffee,file="coffee_clean.csv",row.names=FALSE)
```

## Correlation test between variables
Correlation test of data after cleaning:
```{r echo = TRUE, warning=FALSE, message=FALSE}
coffee.clean <- read.csv("coffee_clean.csv")
cor(coffee[,2:7])
```


# Data visualization

```{r echo = TRUE, warning=FALSE, message=FALSE}
library(gridExtra)
coffee$Qualityclass <- factor(coffee$Qualityclass)
plot1 <- ggplot(data = coffee,aes(x = Qualityclass, y = aroma, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Aroma") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot2 <- ggplot(data = coffee,aes(x = Qualityclass, y = flavor, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Flavor") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot3 <- ggplot(data = coffee,aes(x = Qualityclass, y = acidity, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Acidity") + 
  ylim(7,8) + 
  theme(legend.position = "none")

plot4 <- ggplot(data = coffee,aes(x = Qualityclass, y = category_two_defects, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Category_two_defects") + 
  ylim(-1,10) + 
  theme(legend.position = "none")

plot5 <- ggplot(data = coffee,aes(x = Qualityclass, y = altitude_mean_meters, fill = Qualityclass)) +
  geom_boxplot() +
  labs(x = "Qualityclass", y = "Altitude_mean_meters") + 
  ylim(0,2000)
  theme(legend.position = "none")


## The number of different quality inspection results in each year
plot6 <- ggplot(coffee, aes(x=harvested, fill=as.factor(Qualityclass))) +
  geom_bar(position="dodge", alpha=0.8, stat="count") +
  scale_fill_manual(values=c("Orange", "Blue")) +
  labs(x="Harvested", y="Count", fill="Qualityclass") +
  ggtitle("Qualityclass count by Harvest")

## Merge six charts
## Arrange plot1 to plot6 in a grid of 2 rows and 3 columns
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, nrow=3, ncol=2)
```

# Standardized data
After data cleaning, we standardized the data:
```{r echo = TRUE, warning=FALSE, message=FALSE,results='hide'}
## Creates a logical vector that determines which columns in the data box coffee contain
## numeric data. It uses the function sapply to determine whether the data type of each
## column is numeric.
numeric_cols <- sapply(coffee,is.numeric)
## The columns containing only numerical data in data box coffee are extracted and
## assigned to new data box numeric_coffee
numeric_coffee <- coffee[,numeric_cols]
## A new data box scaled_coffee is obtained by standardizing numerical data in numeric_coffee.
## The standardization process is to transform the data range of different variables into
## the same scale for easy comparison.
scaled_coffee <- as.data.frame(scale(numeric_coffee))
## Add the category_two_defects column from the original data box coffee to scaled_coffee.
scaled_coffee$category_two_defects <- coffee$category_two_defects
## Assign the numerical data in the standardized data frame scaled_coffee back to the
## corresponding column in the original data frame coffee, and overwrite the original data.
coffee[,numeric_cols] <- scaled_coffee
```

# Modeling

## Fit 15 generalized linear models
With Qualityclass as the response variable and aroma, flavor, and acidity as independent variables, 15 different generalized linear models were fitted, and Deviance, and AIC of each model were calculated.
```{r echo=TRUE, warning=FALSE}
model1 <- glm(Qualityclass~aroma+flavor+acidity,family=binomial(link="logit"), data=coffee)
model2 <- glm(Qualityclass~aroma,family=binomial(link="logit"),
              data=coffee)
model3 <- glm(Qualityclass~flavor,family=binomial(link="logit"),
              data=coffee)
model4 <- glm(Qualityclass~acidity,family=binomial(link="logit"),
              data=coffee)
model5 <- glm(Qualityclass~aroma+flavor,family=binomial(link="logit"),
              data=coffee)
model6 <- glm(Qualityclass~flavor+acidity,family=binomial(link="logit"),
              data=coffee)
model7 <- glm(Qualityclass~aroma+acidity,family=binomial(link="logit"),
              data=coffee)
model8 <- glm(Qualityclass~aroma*flavor+acidity,family=binomial(link="logit"),
              data=coffee)
model9 <- glm(Qualityclass~aroma+flavor*acidity,family=binomial(link="logit"),
              data=coffee)
model10 <- glm(Qualityclass~aroma*acidity+flavor,family=binomial(link="logit"),
              data=coffee)
model11 <- glm(Qualityclass~aroma*flavor+aroma*acidity,family=binomial(link="logit"),
              data=coffee)
model12 <- glm(Qualityclass~aroma*flavor+acidity*flavor,family=binomial(link="logit"),
              data=coffee)
model13 <- glm(Qualityclass~aroma*acidity+flavor*acidity,family=binomial(link="logit"),
              data=coffee)
model14 <- glm(Qualityclass~aroma*flavor+acidity*flavor+acidity*aroma,family=binomial(link="logit")
               ,data=coffee)
model15 <- glm(Qualityclass~aroma*flavor*acidity,family=binomial(link="logit"),
              data=coffee)
anova(model1,model2,model3,model4,model5,
      model6,model7,model8,model9,model10,
      model11,model12,model13,model14,model15)
summary(model1)
summary(model8)
AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)
AIC(model5)
AIC(model6)
AIC(model7)
AIC(model8)
AIC(model9)
AIC(model10)
AIC(model11)
AIC(model12)
AIC(model13)
AIC(model14)
AIC(model15)
```
 
   

```{r echo=TRUE, warning=FALSE, message=FALSE}
Modelname <- c("aroma+flavor+acidity","aroma","flavor","acidity",
              "aroma+flavor","flavor+acidity","aroma+acidity","aroma*flavor+acidity",
              "aroma+flavor*acidity","aroma*acidity+flavor",
              "aroma*flavor+aroma*acidity","aroma*flavor+acidity*flavor",
              "aroma*acidity+flavor*acidity","aroma*flavor+acidity*flavor+acidity*aroma",
              "aroma*flavor*acidity")
AIC <- c(model1$aic,model2$aic,model3$aic,model4$aic,
         model5$aic,model6$aic,model7$aic,model8$aic,
         model9$aic,model10$aic,model11$aic,model12$aic,
         model13$aic,model14$aic,model15$aic)
Deviance <- c(model1$deviance,model2$deviance,model3$deviance,
              model4$deviance,model5$deviance,model6$deviance,
              model7$deviance,model8$deviance,model9$deviance,
              model10$deviance,model11$deviance,model12$deviance,
              model13$deviance,model14$deviance,model15$deviance)
table_values <- data.frame(Modelname, Deviance, AIC)
table_values <- as.data.frame(table_values)
table_values %>%
  transmute(Modelname=Modelname, Deviance=Deviance, AIC=AIC) %>%
  kable(caption = '\\label{tab:summary} Deviance and AIC of each model',
booktabs = TRUE, linesep = "", digits = 2) %>%
  kable_styling(font_size = 16, latex_options = "hold_position")

```

## Multicollinearity test of model
VIF (Variance inflation factor) is a statistical index used to detect whether there is collinearity between independent variables. The higher the VIF, the stronger the collinearity between the independent variables, which may lead to instability and inaccuracy of the model.
```{r echo=TRUE}
vif(model1)
vif(model5)
vif(model6)
vif(model7)
vif(model8)
vif(model9)
vif(model10)
vif(model11)
vif(model12)
vif(model13)
vif(model14)
vif(model15)
```

Comprehensive comparison of Deviance, AIC and VIF of each model, we think model1 and model8 are the two models with the best performance.
The two Receiver Operating Characteristic (ROC) curves below show the performance of model1 and model8. 
The areas under the two ROC curves (AUC) are 0.94 and 0.939, which indicate a good classification performance.

```{r echo=TRUE, warning=FALSE, message=FALSE}
coffee.pr <- predict(model1, type="response")
score <- prediction(coffee.pr,coffee$Qualityclass)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
p1 <- ggplot(perfd, aes(x= x, y=y)) + geom_line() +
  xlab("False positive rate") + ylab("True positive rate") +
  ggtitle(paste("model1:Area under the curve:", round(auc@y.values[[1]], 3)))
p1
coffee.pr <- predict(model8, type="response")
score <- prediction(coffee.pr,coffee$Qualityclass)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
p1 <- ggplot(perfd, aes(x= x, y=y)) + geom_line() +
  xlab("False positive rate") + ylab("True positive rate") +
  ggtitle(paste("model8:Area under the curve:", round(auc@y.values[[1]], 3)))
p1
```

# Conclusion

According to the two models we finally select,
$$
model1:\log\left(\frac{p}{1-p}\right) = 0.006953 + 1.207428 \cdot \text{aroma} + 1.967400 \cdot \text{flavor} + 1.152111 \cdot \text{acidity}
$$
$$
model8:\log\left(\frac{p}{1-p}\right) = 0.01235 + 1.27183 \cdot \text{aroma} + 2.04471 \cdot \text{flavor} + 1.13574 \cdot \text{acidity} - 0.55495 \cdot \text{aroma} \cdot \text{flavor}
$$
we believe that the quality of coffee is positively correlated with aroma, acidity and flavor, while the three features of category_two_defects, altitude_mean_meters and harvested have no significant impact on the quality of coffee.

